Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-03-17 paper.tex
Typo
update

@@

\textbf{Cache-Passing Style.}
The definition of Ans is changed to a case class that contains a set of @VS@ and
a cache.
\begin{lstlisting}
case class Ans(vss: Set[VS], cache: Cache)
\end{lstlisting}

@@

In the last section, we just established a computable pushdown control-flow
analysis through refunctionalization and caching. In this section,
we examine how pushdown control-flow is obtained and what we have done to
achieve it.

>>>>

The case class @Cache@ is defined as follow:

@@

The @Cache@ contains two maps @in@ and @out@ which are both mapping from 
configurations to sets of @VS@.

When we enter to function @aeval@

\textbf{Cache-Passing Style.}

The definition of Ans is changed to a case class that contains a set of @VS@ and
a cache.
\begin{lstlisting}
case class Ans(vss: Set[VS], cache: Cache)
\end{lstlisting}

@@

In the last section, we just established a computable pushdown control-flow
analysis through refunctionalization and caching. In this section,
we revisit the pushdown control-flow problem and examine what we have done to
achieve it.
